\section{Control statements} % (fold)
\label{sec:control_statements}

\begin{frame}\frametitle{Control statements}
    \framesubtitle{More control over your program}

    Control statements allow you to do more complicated tasks.

    \begin{itemize}
        \item If
        \item For
        \item While
    \end{itemize}


\end{frame}

\begin{frame}\frametitle{If statements}
    \framesubtitle{}

    Using \texttt{if}, we can execute part of a program conditional on some statement
    being true.

    \codeblock{code/control_if.py}

\end{frame}

\begin{frame}\frametitle{Indentation}
    \framesubtitle{}

    In Python, blocks of code are defined using indentation.

    \vfill

    This means that everything indented after an \texttt{if} statement
    is only executed if the statement is \texttt{True}.

    If the statement is \texttt{False}, the program skips all indented code
    and resumes at the first line of unindented code

    \codeblock{code/control_indentation.py}

\end{frame}

\begin{frame}\frametitle{If-Else statement}
    \framesubtitle{}

    We can add more conditions to the If statement using \texttt{else} and
    \texttt{elif} (short for else if)

    \codeblock{code/control_elif.py}

\end{frame}

\begin{frame}\frametitle{For loops}
    \framesubtitle{}

    Very often, one wants to repeat some action. This can be achieved by a for loop

    \codeblock{code/control_for.py}

    Here, \texttt{range(n)} gives us a \emph{list} with integers $0,\ldots,n-1$.
    More on this later!

\end{frame}

\begin{frame}\frametitle{While loops}
    \framesubtitle{}

    When we not know how many iterations are needed, we can use \texttt{while}.

    \codeblock{code/control_while.py}

\end{frame}

\begin{frame}\frametitle{Continue}
    \framesubtitle{}

    \texttt{continue} continues with the next iteration of the smallest enclosing loop.

    \pause
    \codeblock{code/control_continue.py}

    from: Python documentation

\end{frame}

\begin{frame}\frametitle{Break}
    \framesubtitle{}

    The \texttt{break} statement allows us to jump out of the smallest enclosing
    \texttt{for} or \texttt{while} loop.
    \vfill\pause

    Finding prime numbers:
    \codeblock{code/control_break.py}

    from: Python documentation

\end{frame}

\begin{frame}\frametitle{Pass}
    \framesubtitle{}

    The \texttt{pass} statement does nothing, which can come in handy when you are
    working on something and want to implement some part of your code later.

    \codeblock{code/control_pass.py}

\end{frame}

% section control_statements (end)
