\section{Scipy} % (fold)
\label{sec:scipy}

\begin{frame}
\frametitle{What is SciPy?}
SciPy is a library of algorithms and mathematical tools built to work with NumPy arrays.
\vfill
\begin{itemize}
\item linear algebra - \textit{scipy.linalg}
\item{statistics - \textit{scipy.stats}}
\item{optimization - \textit{scipy.optimize}}
\item{sparse matrices - \textit{scipy.sparse}}
\item{signal processing - \textit{scipy.signal}}
\item{etc.}
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Scipy Linear Algebra}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/linalg.html}}

    Slightly different from numpy.linalg.
    Always uses BLAS/LAPACK support, so could be faster.

    \vfill

    Some more functions.

    \vfill

    Functions can be slightly different.

\end{frame}

% \begin{frame}\frametitle{Scipy Integration}
%     \framesubtitle{}

%     to do

% \end{frame}

\begin{frame}\frametitle{Scipy Optimization}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/optimize.html}}

\begin{itemize}
    \item General purpose minimization: CG, BFGS, least-squares
    \item Constrainted minimization; non-negative least-squares
    \item Minimize using simulated annealing
    \item Scalar function minimization
    \item Root finding
    \item Check gradient function
    \item Line search
\end{itemize}

\end{frame}

\begin{frame}\frametitle{Scipy Statistics}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/stats.html}}

    \begin{itemize}
        \item Mean, median, mode, variance, kurtosis
        \item Pearson correlation coefficient
        \item Hypothesis tests (ttest, Wilcoxon signed-rank test, Kolmogorov-Smirnov)
        \item Gaussian kernel density estimation
    \end{itemize}

See also SciKits (or scikit-learn).

\end{frame}

\begin{frame}\frametitle{Scipy sparse}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/sparse.html}}

    \begin{itemize}
        \item Sparse matrix classes: CSC, CSR, etc.
        \item Functions to build sparse matrices
        \item sparse.linalg module for sparse linear algebra
        \item sparse.csgraph for sparse graph routines
    \end{itemize}

\end{frame}

\begin{frame}\frametitle{Scipy signal}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/signal.html}}

    \begin{itemize}
        \item Convolutions
        \item B-splines
        \item Filtering
        \item Continuous-time linear system
        \item Wavelets
        \item Peak finding
    \end{itemize}

\end{frame}

\begin{frame}\frametitle{Scipy IO}
    \framesubtitle{\url{http://docs.scipy.org/doc/scipy/reference/io.html}}

    Methods for loading and saving data

    \begin{itemize}
        \item Matlab files
        \item Matrix Market files (sparse matrices)
        \item Wav files
    \end{itemize}

\end{frame}




% section scipy (end)
