\section{Strings} % (fold)
\label{sec:strings}

\begin{frame}\frametitle{Strings}
    \framesubtitle{}

    Let's quickly go over \emph{strings}.


    \begin{itemize}
        \item Strings hold a sequence of characters.
        \item Strings are \emph{immutable}
        \item We can slice strings just like lists and tuples
        \item Between quotes or triple quotes
    \end{itemize}

\end{frame}

\begin{frame}\frametitle{Everything can be turned into a string!}
    \framesubtitle{}

    % to edit

    We can turn anything in Python into a string using \texttt{str}.

    \vfill

    This includes dictionaries, lists, tuples, etc.

\end{frame}

\begin{frame}\frametitle{String formatting}
    \framesubtitle{}

    \begin{itemize}
        \item Special characters: \textbackslash n, \textbackslash t,
        \textbackslash b, etc
        \item Add variables: \%s, \%f, \%e, \%g, \%d, or use \texttt{format}
    \end{itemize}

    \codeblock{code/string_format.py}

\end{frame}

\begin{frame}\frametitle{Split}
    \framesubtitle{}

    To split a string, for example, into seperate words, we can use \texttt{split()}

    \codeblock{code/string_split.py}

\end{frame}

\begin{frame}\frametitle{Split}
    \framesubtitle{}

    What if we have a comma seperated file with numbers seperated by commas?

    \codeblock{code/string_split_numbers.py}

    Use the optional argument in \texttt{split()} to use a custom seperator.

    \vfill    \pause

    What to use for a tab seperated file?

\end{frame}

\begin{frame}\frametitle{UPPER and lowercase}
    \framesubtitle{}

    There are a bunch of useful string functions, such as \texttt{.lower()} and \texttt{.upper()} that turn your string in lower- and uppercase.

    Note: To quickly find all functions for a string, we can use \texttt{dir}

    \vfill

    \texttt{text = 'hello'}

    \texttt{dir(text)}

\end{frame}

\begin{frame}\frametitle{join}
    \framesubtitle{}

    Another handy function: \texttt{join}.

    We can use join to create a string from a list.

    \codeblock{code/string_join.py}

\end{frame}

% section strings (end)
