\section{Wrap up}

\begin{frame}\frametitle{Zen of Python}

    \codeblock{code/wrapup_this.py}

\end{frame}

\begin{frame}\frametitle{Have you fallen in love with Python?}

    `There's nothing wrong with falling in love with a programming language for her looks. I mean, let's face it - Python does have a rockin' body of modules, and a damn good set of utilities and interpreters on various platforms. Her whitespace-sensitive syntax is easy on the eyes, and it's a beautiful sight to wake up to in the morning after a long night of debugging. The way she sways those releases on a consistent cycle - she knows how to treat you right, you know?...'

    \url{https://www.quora.com/Have-I-have-fallen-in-love-with-Python-because-she-is-beautiful}

\end{frame}

\begin{frame}\frametitle{Project and portfolio}

    Please remember: projects and portfolios due next Thursday at noon.

    Coursework checklist:
    \begin{itemize}
        \item Project code (\textbf{py} file(s) or \textbf{zip}).
        \item Project write-up (\textbf{pdf} file (no word!)).
        \item All scripts you wrote for class (\textbf{zip} with all \textbf{py} files). No write up necessary.
    \end{itemize}

\end{frame}

\begin{frame}\frametitle{Feedback}
    \framesubtitle{}

    Thanks a lot!

    Hope you enjoyed the class and learnt a lot!

    \vfill

    Another feedback form:
    \begin{center}
            \url{goo.gl/3onaCL}
    \end{center}
    or via course website

    \vfill

    \texttt{Questions?}

\end{frame}